Combinatorics of the geometry of Wilson loop diagrams I: equivalence classes via matroids and polytopes

### 2019-08-09 GWLDCI.tex
made changes to GNproof according to Karen's comments; removed non-crossing partition reference
replace "not independent" with "is dependent"

It is worth remarking that these maximal decompositions correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.

@@

\begin{lem} \label{maxexactcomplementrank}
Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is not an independent flat in $W$.
\item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
\item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
\end{enumerate} 
\end{lem}

@@

We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is not independent.

@@

For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram of $W$. By Lemma \ref{lem decompose flat}(1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
\begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an independent set. We show that $\Prop(C) = P^c$, thus forcing $S$ to be empty and implying that $F(P^c) = C$, i.e. $F(P^c)$ is a cyclic flat. Note that $C$ must be non-empty since $F(P^c)$ is non-empty and not independent (by part (1)).

>>>>

%It is worth remarking that these maximal decompositions correspond to non-crossing partitions of the Wilson loop diagram, in the sense discussed in \cite{positroids13}.

@@

\begin{lem} \label{maxexactcomplementrank}
Let $W = (\cP, [n])$ be an admissible Wilson loop diagram, and $P \subseteq \cP$. Then: \begin{enumerate}
\item If $(P,V(P))$ is an exact subdiagram of $W$, then $F(P^c)$ is a dependent flat in $W$.
\item If $(P,V(P))$ is a maximal exact subdiagram of $W$, then $F(P^c)$ is a cyclic flat in $W$.
\item If $(P,V(P))$ is an exact subdiagram in $W$, then $\rk(F(P^c)) = |P^c|$.
\end{enumerate} 
\end{lem}

@@

We know from Lemma~\ref{lem facts about WLD matroids} that $F(P^c)$ is always a flat, so for part (1) we only need to show that $F(P^c)$ is dependent.

@@

For part (2), suppose that $(P, V(P))$ is a maximal exact subdiagram of $W$. By Lemma \ref{lem decompose flat}(1) and Corollary \ref{classifyflats} we can decompose $F(P^c)$ as
\begin{equation}\label{eq decompose F}V(P)^c = F(P^c) = C \sqcup S = F(\Prop(C)) \sqcup S,\end{equation}
where $C$ is the largest cyclic flat contained in $F(P^c)$ and $S$ is an independent set. We show that $\Prop(C) = P^c$, thus forcing $S$ to be empty and implying that $F(P^c) = C$, i.e. $F(P^c)$ is a cyclic flat. Note that $C$ must be non-empty since $F(P^c)$ is non-empty and dependent (by part (1)).
